\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-03-19 syscoin_4.0/article.tex
appendix
eip 1559

Figure 1 shows the difference between a regular
blockchain and Syscoin’s Z-DAG implementation. Syscoin
now has two consensus layers: In the first layer, a ZDAG graph of transactions are represented in the mempool
without a block, providing settlement in real-time. The secondary layer provides confirmation and conflict resolution
preventing double-spend events through existing Proof of
Work consensus.

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/eth_tx_vs_gas.png}
\label{fig:eth_tx_vs_gas}
\caption{eth tx vs gas} 
\end{figure}

@@

@@

>>>>

\begin{figure}[h!]
\includegraphics[width=3in]{img/current_vs_zdag.png}
\label{fig:current_vs_zdag}
\caption{Current Blockchain design vs Z-DAG} 
\end{figure}

Figure \ref{fig:current_vs_zdag}  shows the difference between a regular
blockchain and Syscoin’s Z-DAG implementation. Syscoin
now has two consensus layers: In the first layer, a ZDAG graph of transactions are represented in the mempool
without a block, providing settlement in real-time. The secondary layer provides confirmation and conflict resolution
preventing double-spend events through existing Proof of
Work consensus.

@@

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_gas_costs_eip_1559.png}
\label{fig:sysx_gas_costs_eip_1559}
\caption{sysx gas costs eip 1559} 
\end{figure}

@@

\section{EIP 1559}

EIP-1559 is a new pricing mechanism for the Ethereum protocol that includes a stationary network fee during states of no congestion which dynamically adjusts during states of congestion. The original gas fee model uses a auction system where miners choose transactions with the highest bids. This has led to several inefficiencies such as instability of blockchains with no reward, needless delays, fee overpayment, and mismatch fee levels between volatility ad social cost.

The basic premise of the new proposal begins with setting the base fee which increases when the network capacity exceeds the target per-block gas usage, and decreases when the capacity is below the target. The calculation of the updated basefee, $b_{k}$ at the $k^{th}$ block,  is as follows:

\begin{equation}
b_{k} = b_{k-1}\left(\dfrac{1+ \delta}{k}\right), 
\end{equation}
where $\delta = usage - target~gas~fee$, and $k = (target)/(basefee~max~change)$
